Reactor Design Compilation

### 2019-07-03 msr-list.tex
fixed bibliography

\section{Molten Salt Breeder Reactor (MSBR)}
The MSBR builds on the MSRE, adding a conversion ratio high enough to classify the MSBR as a true breeder reactor.  It features a higher power in its design specifications, at the cost of a low graphite lifetime.  Additionally, it has a lesser fuel vol\% than the MSRE, and two fewer control rods.

@@

The Transatomic reactor has two important differences from other thermal-spectrum MSRs in this review.  It changes the fuel salt mixture, and forgoes a graphite moderator for something with a better lifespan under the conditions of the reactor \cite{robertson_assessment_2017}.

>>>>

\section{Molten Salt Breeder Reactor (MSBR)}
The MSBR builds on the MSRE, adding a conversion ratio high enough to classify the MSBR as a true breeder reactor.  It features a higher power in its design specifications, at the cost of a low graphite lifetime.  Additionally, it has a lesser fuel vol\% than the MSRE, and two fewer control rods. \cite{bettis_design_1970}, \cite{whatley_engineering_1970}

@@

The Transatomic reactor has two important differences from other thermal-spectrum MSRs in this review.  It changes the fuel salt mixture, and forgoes a graphite moderator for something with a better lifespan under the conditions of the reactor \cite{robertson_assessment_2017} \cite{transatomic_power_corporation_neutronics_2016} \cite{transatomic_power_corporation_technical_2016}.
